\documentclass{report}

\input{preamble}
%\input{macros}
%\input{letterfonts}

\title{\huge{P-16:}\\Leaderboard Project Plan}
\date{March 5, 2025}

\begin{document}
\maketitle
\section*{Project Timeline}
This timeline will cover the planning aspect of all tasks within LEADERBOARD branch. Each member is expected to contribute \(3\times45\) minutes per week.

\section{Planning and Design}
\begin{itemize}
    \item Create planning documents for LEADERBOARD branch.
    \begin{itemize}
        \item Create a outline and rough dates for when tasks are estimated to be finished
        \item \textbf{Deadline:} March 5, 2025
    \end{itemize}
    \item Design use case diagrams
    \begin{itemize}
        \item Create draft then create final of the use case diagrams.
        \item \textbf{Deadline:} March 6, 2025
    \end{itemize}
    \item Design class structure diagrams.
    \begin{itemize}
        \item Create a general class structure diagram for classes in LEADERBOARD.
        \item \textbf{Deadline:} March 6, 2025
    \end{itemize}
    \item Create use case descriptions document
    \begin{itemize}
        \item Identify and provide details to different use cases.
        \item \textbf{Deadline:} March 6, 2025
    \end{itemize}
    \item Review and submit documents for iteration 1:
    \begin{itemize}
        \item Team review, spell checking, format checkin, proofread, then submit to D2L dropbox.
        \item \textbf{Deadline:} March 6, 2025
    \end{itemize}
\end{itemize}
\subsection*{Milestones:}
\begin{itemize}
    \item team 6 : : iteration 1: March 7, 2025
\end{itemize}
\section{Development and Implementation}
\begin{itemize}
    \item \textbf{Objective:} Develop and implement a Leaderboard system to display the ranking of all players, with player profiles, and update rankings.
    \item \textbf{Duration:} March 8, 2025 - April 11, 2025 (Post-iteration 1 to iteration 3 deadline)
    \item \textbf{Key Features:}
    \begin{itemize}
        \item Display players with rank, username, win/loss/points stats.
        \item Update rankings
        \item Allow to search players in Leaderboad.
        \item Allow users to change the filter of the Leaderboard. (descending/ascending order)
        \item Allow the users to change the ranking criteria.
        \item Intergrate with GUI and other systems of the app.
    \end{itemize}
\end{itemize}
The Development and Implementation will be divided into phase: Setup, Core Development, Integration, Testing, and Review. Tasks are assigned to balance workload among all team members.
% phase 1
\subsection*{Phase 1: Setup}
\begin{itemize}
    \item \textbf{Duration:} March 8, 2025 - March 12, 2025
    \item \textbf{Goal:} Establish rough skeleton code and finalize design for LEADERBOARD
\end{itemize}
Tasklist:
\begin{itemize}
    \item Git Repository Setup
    \begin{itemize}
        \item \textbf{Start Date:} March 8, 2025
        \item \textbf{End Date:} March 8, 2025
        \item \textbf{Estimated Time:} 1 hour
    \end{itemize}
    \item Finalize class structure design: Adjust class diagram based on feedback
    \begin{itemize}
        \item \textbf{Start Date:} March 9, 2025
        \item \textbf{End Date:} March 10, 2025
        \item \textbf{Estimated Time:} 3 hours    
    \end{itemize}
    \item Stub database interface: Simulate fetch rankings
    \begin{itemize}
        \item \textbf{Start Date:} March 10, 2025
        \item \textbf{End Date:} March 11, 2025
        \item \textbf{Estimated Time:} 3 hours
    \end{itemize}
    \item Plan GUI: Create a sketch for the LEADERBOARRD GUI
    \begin{itemize}
        \item <tasks>
        \item \textbf{Start Date:} March 11, 2025
        \item \textbf{End Date:} March 12, 2025
        \item \textbf{Estimated Time:} 3 hours
    \end{itemize}
    
\end{itemize}
\subsection*{Milestones:}
\begin{itemize}
    \item Setup complete: March 12, 2025
\end{itemize}
% phase 2
\subsection*{Phase 2: Core Development}
\begin{itemize}
    \item \textbf{Duration:} March 13, 2025 - March 25, 2025
    \item \textbf{Goal:} Implement core systems for LEADERBOARD
\end{itemize}
Tasklist:
\begin{itemize}
    \item Implement a class to read and store player details
    \begin{itemize}
        \item \textbf{Start Date:} Match 13, 2025
        \item \textbf{End Date:} March 16, 2025
        \item \textbf{Estimated Time:} 5 hours
    \end{itemize}
    \item Create a sorting class that sorts by wins or any other criteria
    \begin{itemize}
        \item \textbf{Start Date:} March 14, 2025
        \item \textbf{End Date:} March 18, 2025
        \item \textbf{Estimated Time:} 8 hours
    \end{itemize}
    \item Implement displaying Leaderboard
    \begin{itemize}
        \item \textbf{Start Date:} March 14, 2025
        \item \textbf{End Date:} March 18, 2025
        \item \textbf{Estimated Time:} 8 hours
    \end{itemize}
    \item Simulate ranking updates either automatically or manually by pressing update button
    \begin{itemize}
        \item \textbf{Start Date:} March 19, 2025
        \item \textbf{End Date:} March 22, 2025
        \item \textbf{Estimated Time:} 4 hours
    \end{itemize}
    \item Basic GUI display
    \begin{itemize}
        \item \textbf{Start Date:} March 20, 2025
        \item \textbf{End Date:} March 25, 2025
        \item \textbf{Estimated Time:} 5 hours
    \end{itemize}
\end{itemize}
\subsection*{Milestones:}
\begin{itemize}
    \item Leaderboard prototype: March 25, 2025
\end{itemize}
% phase 3
\subsection*{Phase 3: Integration}
\begin{itemize}
    \item \textbf{Duration:} March 26, 2025 - April 1, 2025
    \item \textbf{Goal:} Connect leaderboad to other featues and GUI
\end{itemize}
Tasklist:
\begin{itemize}
    \item Integrate with other matchmaking: Add a method to receive game results from matchmaking stub, then udpate leaderboard
    \begin{itemize}
        \item \textbf{Start Date:} March 26, 2025
        \item \textbf{End Date:} March 29, 2025
        \item \textbf{Estimated Time:} 6 hours
    \end{itemize}
    \item Enchange GUI interaction: Maybe add clickable names to view profiles (i.e. Clash Royale)
    \begin{itemize}
        \item \textbf{Start Date:} March 27, 2025
        \item \textbf{End Date:} March 31, 2025
        \item \textbf{Estimated Time:} 6 hours
    \end{itemize}
    \item Link player stats to the viewed profile
    \begin{itemize}
        \item \textbf{Start Date:} March 28, 2025
        \item \textbf{End Date:} April 1, 2025
        \item \textbf{Estimated Time:} 4 hours
    \end{itemize}
    \item Test integration
    \begin{itemize}
        \item \textbf{Start Date:} March 30, 2025
        \item \textbf{End Date:} April 1, 2025
        \item \textbf{Estimated Time:} 3 hours
    \end{itemize}


\end{itemize}
\subsection*{Milestones:}
\begin{itemize}
    \item Integated LEADERBOARD: April 1, 2025
\end{itemize}
% phase 4
\subsection*{Phase 4: Testing}
\begin{itemize}
    \item \textbf{Duration:} April 2, 2025 - April 8, 2025
    \item \textbf{Goal:} Ensure there are no bugs.
\end{itemize}
Tasklist:
\begin{itemize}
    \item Create unit tests using JUnit to test ranking updates and also update player stats
    \begin{itemize}
        \item \textbf{Start Date:} April 2, 2025
        \item \textbf{End Date:} April 5, 2025
        \item \textbf{Estimated Time:} 6 hours
    \end{itemize}
    \item Test GUI functions
    \begin{itemize}
        \item \textbf{Start Date:} April 3, 2025
        \item \textbf{End Date:} April 6, 2025
        \item \textbf{Estimated Time:} 4 hours
    \end{itemize}
    \item Test ranking logic: Test the soring methods and updates
    \begin{itemize}
        \item \textbf{Start Date:} April 4, 2025
        \item \textbf{End Date:} April 7, 2025
        \item \textbf{Estimated Time:} 3 hours
    \end{itemize}
    \item Full system test
    \begin{itemize}
        \item \textbf{Start Date:} April 5, 2025
        \item \textbf{End Date:} April 8, 2025
        \item \textbf{Estimated Time:} 3 hours
    \end{itemize}
\end{itemize}
\subsection*{Milestones:}
\begin{itemize}
    \item LEADERBOARRD tested: April 8, 2025
\end{itemize}
% phase 5
\subsection*{Phase 5: Review}
\begin{itemize}
    \item \textbf{Duration:} 
    \item \textbf{Goal:} 
\end{itemize}
Tasklist:
\begin{itemize}
    \item Update documentation
    \begin{itemize}
        \item \textbf{Start Date:} April 9, 2025
        \item \textbf{End Date:} April 9, 2025
        \item \textbf{Estimated Time:} 2 hours
    \end{itemize}
    \item Full code review
    \begin{itemize}
        \item \textbf{Start Date:} April 9, 2025
        \item \textbf{End Date:} April 10, 2025
        \item \textbf{Estimated Time:} 3 hours
    \end{itemize}
    \item Record video demonstration
    \begin{itemize}
        \item \textbf{Start Date:} April 9, 2025
        \item \textbf{End Date:} April 10, 2025
        \item \textbf{Estimated Time:} 3 hours
    \end{itemize}
    \item Submit documents
    \begin{itemize}
        \item \textbf{Start Date:} April 10, 2025
        \item \textbf{End Date:} April 11, 2025
        \item \textbf{Estimated Time:} 1 hour
    \end{itemize}


\end{itemize}
\subsection*{Milestones:}
\begin{itemize}
    \item Submission: April 11, 2025
\end{itemize}

\section*{Final Notes}
Start coding on March 8, 2025, the earlier the better. Hold weekly meeting with other team leader working on other features.
Hold scrum meetings with own team. Branch early and branch often, and commit frequently to GitLab.


\end{document}